### 2024-08-11 paper.tex
finish showing that span of Jordan basis is big enough

\par Now, we want to show that this chain is linearly independent from the chains we have already listed.
Because \(A^{r + n + P} e_{i_0, \lambda_{i_0}}\) is in the span of the chains we have already listed, it suffices to show that \(A^k e_{i_0, \lambda_{i_0}}\) is linearly independent of the previous chains, for all \(k < r + n + P\).
Indeed, by the definition of \(P\), we have that \(A^k e_{i_0, \lambda_{i_0}}\) has a nonzero \(e_{ij}\)-component, for some \(i\) with \(q_i < n + r\); and the chains we have listed previously all have \(e_{ij}\)-component equal to zero for \(i\) with \(q_i < n + r\).

@@

To see that this is linearly independent of what came before... TODO.

@@

\par TODO: where did I use the fact that \(n + \max_i p_i \geq q_{i_0} + p_{i_0}\)?

>>>>

\par Now, it is clear that \(e_{i_0, p_{i_0} + q_{i_0} + i}\) is in the span of the chains we have listed so far for each \(i \geq 1\).
It is also clear that \(b' \leftshift k\) is in the span, for each \(k \geq 0\).

@@

Clearly we then have \(e_{i'j}\) in the span of the chains we have listed, for \(i' \leq i\).

@@

\par Now, we want to show that for each \(j\), \(e_{ij}\) is in the span of the chains we've listed so far.
Since \(A^{q_i + \max_{k > i} p_k} v_i\) has rows \(k\) zeroed out for \(k \geq i\), our inductive hypothesis tells us that \(A^{q_i + \max_{k > i} p_k} v_i \rightshift q_i + \max_{k > i} p_k\) is in the span of the chains already listed.
So it suffices to show that the closure of \(\langle v_i \rangle\) under action by \(A\) contains the span of \(e_{ij}\).
And \(A^{n + r - q_i} e_{i_0, \lambda_{i_0}}\) is also in the span of chains already listed, so it suffices to show that the closure of \(\langle \sum_k b'_{ik} e_{i,k + q_i}\rangle \) under action by \(A\) contains \(\langle e_{ij}\rangle\).
And this just follows from the fact that \(b'_{i,p_i}\) is nonzero.
\par Now, I've shown that my purported Jordan basis has a large enough span; to show that it is indeed a Jordan basis I just need to count the number of vectors and show that we obtain \(m + n\).
TODO: do this.
